\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

%%%%%%%%%%%%
\subsection{Model Validation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Model Validation}\label{section:validation:results}

Numerical simulations performed for this work were conducted with the next generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}. This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displecement, viscous crossflow etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}. Two test-cases
